Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-08-29 paper/paper.tex
more paper edits Tested everything on quipu.

We have found that the deterministic simulations of the protein
reaction sequence discussed above results in robust oscillatory
behavoir of polar selection and oscillation in not only symmetrical
shapes, such as the wildtype pill shape, but also in very
assymetrical, flatttened cells, such as those studied by Mannik.
After the lower stability limit of
section~\ref{sec:stability-analysis} has been surpassed, this
qualitative behavoir doesn't seem to have size dependence until cells
reach sizes that have more than twice the dimensions of the Mannik
cells.  At this point the robust oscillations, while still evident,
begin to lose their consistanty.  The Mannik reported cells already
seem to be rather large (wild type cells are typically smaller than
those observed my Mannik
\cite{kubitschek1990cell,kubitschek1968linear,mannik2012robustness}),
so we left off simulating cells any larger than twice this size.

This differs with Mannik's experimental findings
that show much less regular behavoir, with a large variation in the
location of maxima.  On the other hand, our stochastic simulations
show both robust pole to pole oscillations in the symmetric cells and
irregular behavoir in the assymetrical shapes, agreeing well with
Mannik's experimental findings.

>>>>

We have found that the deterministic simulations of the protein
reaction sequence discussed above results in robust oscillatory
behavoir of polar selection and oscillation in not only symmetrical
shapes, such as the wildtype pill shape, but also in very
assymetrical, flatttened cells, such as those studied by Mannik.
After the lower stability limit of
section~\ref{sec:stability-analysis} has been surpassed, this
qualitative behavoir doesn't seem to have size dependence until cells
reach sizes that have more than twice the dimensions of the Mannik
cells.  At this point the robust oscillations, while still evident,
begin to lose their consistanty.  The Mannik reported cells already
seem to be rather large (wild type cells are typically smaller than
those observed my Mannik
\cite{kubitschek1990cell,kubitschek1968linear,mannik2012robustness}),
so we left off simulating cells any larger than twice this size. The
movies show sharp peaks of MinD in specific locatations, typically at
the edges of the cell and in regions of high radius of curvature,
followed by a spreading out of the MinD out into the cell, with no
real bias towards any location, until it aggregates again in a
specific location at the opposite edge of the cell, maximizing there.
The pattern is repeated again and again with surprising consistency,
which can be seen on the right of Figure~\ref{box-mannik}.  This is
the same plotting method as our box plots above, here showing
stochastic and deterministic simulations of cells that are the same
shape and size of one of Mannik's reported cells.

The findings differ with Mannik's experimental findings
that show much less regular behavoir, with a large variation in the
location of maxima.  On the other hand, our stochastic simulations
show both robust pole to pole oscillations in the symmetric cells and
irregular behavoir in the assymetrical shapes, agreeing well with
Mannik's experimental findings.
